The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/manuscript.Rmd
messing with conclusion arrangement

With our caribou case stuyd, we show that (1) multilayer social networks can be,
but are not always, scale dependent and (2) that the use of multilayer networks
could be useful for identifying habitat or season-specific social processes. Our
analyses of social, spatial, and temporal scales in multilayer network framework
highlight potential to identify scales at which variation in properties of
layers within a multilayer network show the most variability. Our analysis of
caribou multilayer networks incorporated high resolution GPS telemetry data and
spatial landcover data, thus allowing us ground our broader discussion of
multilayer networks in the context of observed animal social networks.
<!--QW: I am not very happy with this paragraph, but it's a start -->

Multilayer networks remain a nascent tool in animal behavioural ecology. We
demonstrate novel analyses that vary social, spatial, and temporal scale within
a multilayer framework and we discuss the potential integration of individual
phenotypes and fitness, collective movememtn, and habitat selection for future
analyses considering spatial ecology  using multilayer networks. Silk et al.
(2018) summarized some key multilayer questions in animal behaviour research.
While these questions are important for linking animal behaviour and multilayer
networks, we summarize our perspectives on the future of multilayer networks
with an additional set of questions posed through the lense of spatial ecology
that are relevant to the promise and problem of scale in mutlilayer networks:

>>>>

Multilayer networks remain a nascent but powerful tool in animal behavioural ecology. We
demonstrate novel analyses that vary social, spatial, and temporal scale within
a multilayer framework. In our caribou case study, we show that (1) multilayer social networks can be,
but are not always, scale dependent, and (2) the use of multilayer networks
could be useful for identifying habitat or season-specific social processes. Our
analyses of social, spatial, and temporal scales in multilayer network framework
highlight potential to identify scales at which different properties of
layers within a multilayer network show the most variability. Furthermore, we discuss the potential integration of individual phenotypes and fitness, collective movement, and habitat selection for future
analyses considering spatial ecology  using multilayer networks.

<!--QW: I am not very happy with this paragraph, but it's a start -->

Our analysis of caribou multilayer networks incorporated high resolution GPS telemetry data and
spatial landcover data, thus allowing us to ground our broader discussion of
multilayer networks in the context of observed animal social networks.

Silk et al. (2018) summarized some key multilayer questions in animal behaviour research.
While these questions are important for linking animal behaviour and multilayer
networks, we summarize our perspectives on the future of multilayer networks
with an additional set of questions posed through the lense of spatial ecology
that are relevant to the promise and problem of scale in mutlilayer networks:
